Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-04-27 article.tex
EOD

@@

\richel{Check against stupidity}
Regarding human viruses, we do not know the selection pressure
exerted by the human immune system.
We do know that this selection pressure is 
limited for seasonal influenza \cite{han2019individual},
but this study does not look into the evolution of TMHs
\richel{Use this study, if COVID-19 dataset is too weak}.
For COVID-19, there is preliminary evidence that the strongest
selection pressure is upon ORF3 (an ion channel and a viroporin)
and ORF8 (unknown function). ORF3 has 3 TMHs that appear irrelevant for
the natural selection of COVID-19.
We predict that evolutionary conservation is strongest 
for regions that are essential for viral proteins'
functions (such as catalytic binding sites), instead of TMHs.
Because these essential regions are rare in a viral proteome,
and differ widely between pathogens, we expect that the human immune system
is not tailored to detect these sites, similar to the aforementioned
influenza study. 
TMHs, however, have less 
functional constraints compared to catalytic regions,
and as such are more general. 
Because TMHs are more general,
we expect it for the immune system to pay off to be more attentive towards
TMHs.
For viral TMHs that are undetected by most human haplotypes, we
expect these to be conserved, to remain avoiding detection.
For viral TMHs that are detected by most human haplotypes, we
expect there to be a higher mutation rate, to avoid detection.
Additionally, viruses are not only selected for their evasion of an 
immune response, yet are selected to have a high reproductive value.
Because the strength of the evolutionary signal is unknown,
we use a strong data set to be able to detect it.

>>>>

\paragraph{Use of protein data in phylogenetics}

In DNA, select
To detect the signature of selection \cite{murrell2015gene}

From \cite{anisimova2009investigating}, I quote: 
although most proteins evolve under purifying selection most of the time, 
positive selection may affect some lineages, and during episodes of adaptive 
evolution, only a small fraction of sites in the protein have the capacity 
to increase the 'fitness' of the protein via AA 
replacements (e.g., Gillespie 1991; Li 1997; Messier and Stewart 1997; 
Pupko and Galtier 2002). 
Thus, approaches assuming constant selective pressure over time and 
over sites lack power in detecting genes affected by positive 
selection (Yang and Bielawski 2000).

Commonly, DNA is used in phylogenetics.
Some argue that the proteome is superior \cite{diz2012proteomics}:

@@

\richel{Check against stupidity}
Regarding human viruses, we do not know the selection pressure
exerted by the human immune system.
We do know that this selection pressure is 
limited for seasonal influenza \cite{han2019individual},
but this study does not look into the evolution of TMHs
\richel{Use this study, if COVID-19 dataset is too weak}.
For COVID-19, there is preliminary evidence that the strongest
selection pressure is upon ORF3 (an ion channel and a viroporin)
and ORF8 (unknown function) \cite{velazquez2020positive}. 
Of these two proteins, ORF3 has 3 TMHs,
yet selection was only detectable in non-TMHs.
We predict that evolutionary conservation is strongest 
for regions that are essential for viral proteins'
functions (such as catalytic binding sites), instead of TMHs.
Because these essential regions are rare in a viral proteome,
and differ widely between pathogens, we expect that the human immune system
is not tailored to detect these sites, similar to the aforementioned
influenza study. 
TMHs, however, have less 
functional constraints compared to catalytic regions,
and as such are more general. 
Because TMHs are more general,
we expect it for the immune system to pay off to be more attentive towards
TMHs.
For viral TMHs that are undetected by most human haplotypes, we
expect these to be conserved, to remain avoiding detection.
For viral TMHs that are detected by most human haplotypes, we
expect there to be a higher mutation rate, to avoid detection.
Additionally, viruses are not only selected for their evasion of an 
immune response, yet are selected to have a high reproductive value.
Because the strength of the evolutionary signal is unknown,
we use a strong data set to be able to detect it.
